### 2020-08-11 3_implementation.tex
Fiddle with figures.
Update StarPU text.

@@

Task-based systems include OmpSs~\cite{OmpSs11}, OpenMP
4.0~\cite{OpenMPSpec40}, PaRSEC~\cite{PARSEC13, PARSEC_DTD},
Realm~\cite{Realm14}, Regent~\cite{Regent15}, and
StarPU~\cite{StarPU11}. Though the details vary, these systems
typically provide implicit parallelism, where tasks are enumerated
sequentially (in program order) and the dependencies between tasks are
analyzed automatically to construct a \emph{dependence graph} that
guides the execution of tasks. PaRSEC provides two modes,
\emph{dynamic task discovery} (DTD)~\cite{PARSEC_DTD}, which operates
as above, and \emph{parameterized task graphs} (PTG)~\cite{PARSEC13},
where the dependence graph is constructed automatically from an
analytical representation of the task graph. Realm (unlike the others
above) is explicitly parallel and requires tasks to be connected
explicitly via \emph{events}.

Among distributed task-based systems, there can be a scalability
bottleneck due to enumerating tasks sequentially. PaRSEC and StarPU
allow users to omit tasks that are not
directly connected in the dependence graph. The program is replicated
(for efficiency of analysis), but each task is executed only
once. Because the dynamic checks to see if a task should be executed
are not free of cost, we also provide a PaRSEC implementation (labeled \lstinline{shard}) hand-written to avoid all
such checks. Regent performs an equivalent optimization at compile
time~\cite{ControlReplication17} that does not require user
intervention.

>>>>

Task-based systems include OmpSs~\cite{OmpSs11}, OpenMP
4.0~\cite{OpenMPSpec40}, PaRSEC~\cite{PARSEC13, PARSEC_DTD},
Realm~\cite{Realm14}, Regent~\cite{Regent15}, and
StarPU~\cite{StarPU11}. Though the details vary, these systems
typically provide implicit parallelism, where tasks are enumerated
sequentially (in program order) and the dependencies between tasks are
analyzed automatically to construct a \emph{dependence graph} that
guides the execution of tasks. PaRSEC provides two modes,
\emph{dynamic task discovery} (DTD)~\cite{PARSEC_DTD}, which operates
as above, and \emph{parameterized task graphs} (PTG)~\cite{PARSEC13},
where the dependence graph is constructed automatically from an
analytical representation of the task graph. Realm (unlike the others
above) is explicitly parallel and requires tasks to be connected
explicitly via \emph{events}. StarPU, in addition to its usual,
implicitly parallel mode, also provides a mode where MPI is used for
synchronization (and is thus explicitly parallel).

Among distributed task-based systems, there can be a scalability
bottleneck due to enumerating tasks sequentially. PaRSEC and StarPU
allow users to omit tasks that are not directly connected in the
dependence graph. The program is replicated (for efficiency of
analysis), but each task is executed only once. Because the dynamic
checks to see if a task should be executed are not free of cost, we
also provide versions of the PaRSEC and StarPU implementations
(labeled \lstinline{shard} and \lstinline{expl}, respectively)
hand-written to minimize such costs. PaRSEC \lstinline{shard} uses the
DTD mode but manually minimizes dynamic checks. StarPU
\lstinline{expl} uses the MPI integration described above. We see in
Section~\ref{subsec:scalability} that such modifications are needed to
achieve optimal scalability. Regent performs an equivalent
optimization at compile time~\cite{ControlReplication17} that does not
require user intervention and preserves the original, implicitly
parallel programming model of the language.

@@
